Response to the defense feedback

### 2021-06-18 Chapter-5/Chapter-5.tex
Updates from Overleaf

While many existing works can detect side-channel leakages, few
of them can assess the severity levels of these
vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
these tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.  Often the over-approximated estimate is very far away from the amount of real leakage.
For example, CacheAudit~\cite{182946} estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report that some leakages can leak lots of information, it does not mean the program has truly severe side-channel vulnerabilities.

@@

\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by AFL and Valgrind, we use a bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset LMA (Load Memory Address) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

>>>>

While many existing works can detect side-channel leakages, few
of them can assess the severity levels of these
vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
these tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. 
For example, CacheAudit~\cite{182946} estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report that some leakages can leak lots of information, it does not mean the program has truly severe side-channel vulnerabilities.

@@

\subsection{Step 2: Address Recording}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by AFL and Valgrind, we use a bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset LMA (Load Memory Address) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.
